Bird beak's elaboration and innovation

### 2025-04-07 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

@@

>>>>

## Getting distributions
elaborations_global <- get.disparity(get.subsets(results$super_results_phylo$position, subsets = "phylogeny"), concatenate = FALSE)[[1]][, sample(1:4000, 100)]
innovations_global <- get.disparity(get.subsets(results$super_results_phylo$distance, subsets = "phylogeny"), concatenate = FALSE)[[1]][, sample(1:4000, 100)]

write.csv(elaborations_global, file = "../Data/Processed/elaborations_distributions.csv")
write.csv(innovations_global, file = "../Data/Processed/elaborations_distributions.csv")

@@

## Different scales
elaboration_innovation_scale <- data.frame("median_elaboration_superorder" = ploting_data_superorder$median_elaborations,
                                           "median_elaboration_order" = ploting_data_order$median_elaborations,
                                           "median_innovation_superorder" = ploting_data_superorder$median_innovations,
                                           "median_innovation_order" = ploting_data_order$median_innovations,
                                           "median_distance_centre_superorder" = ploting_data_superorder$distances_to_centre,
                                           "median_distance_centre_order" = ploting_data_order$distances_to_centre)
write.csv(elaboration_innovation_scale, file = "../Data/Processed/elaboration_innovation_scale.csv")
